Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Updated beechnut
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@33 db7c848b-7755-4df2-b763-8796797afa52

\begin{figure}[ht]\center
  \includegraphics[height=.37\columnwidth]{images/spikes512}\hfil
  \includegraphics[height=.37\columnwidth]{images/beechnut}
  \caption{\label{fVolumes}Volumes used for object distribution benchmarks:
    spike frequencies of a three million neuron electrical simulation at
    437x240x512 unsigned byte (51MB, left) and an MRI scan of a beechnut at
    1024x1024x1546 unsigned short (3GB, right) resolution}
\end{figure}

>>>>

\begin{figure}[ht]\center
  \includegraphics[height=.44\columnwidth]{images/spikes512}\hfil
  \includegraphics[height=.44\columnwidth]{images/beechnut}
  \caption{\label{fVolumes}Volumes used for object distribution benchmarks:
    spike frequencies of a three million neuron electrical simulation at
    437x240x512 unsigned byte (51MB, left) and an MicroCT scan of a beechnut at
    1024x1024x1546 unsigned short (3GB, right) resolution}
\end{figure}
